---
title: "The Correlation of Daily Sales for Tenant Synergy Analysis"
author: "Nabiilah Ardini Fauziyyah"
date: "8/16/2019"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    highlight: textmate
    number_sections: false
    df_print: paged
---
<style>
h1.title {
  text-align: center;
}
h4.author {
  text-align: center;
}
h4.date {
  text-align: center;
}

body {
text-align: justify}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
```

## Import Library

```{r message=FALSE, warning=FALSE}
library(tidyr)
library(dplyr)
library(lubridate)
```

## Read Data

To explain the process of using the correlation of daily sales/revenues for tenant synergy analysis, we use a dummy data: 

```{r message=FALSE, warning=FALSE}
dummy <- read.csv("data_input/dummy-corr.csv") %>%
  mutate(Date = mdy(Date))
head(dummy)
```

Above is the report of daily revenues for each tenant. Below are the column descriptions:

* `No`: number of rows
* `Tenant`: name of tenant
* `Group`: group assigned for each tenant
* `Date`: date of daily sales recorded
* `Revenue`: daily sales/revenue

There are assumption applied in using this approach:

* assuming there is only one type of crowd
* assuming that each tenant has similar revenues ~ number of costumer: one type of tenant whose revenues is high may not give higher amount of costumer than the one which has lower revenues with lower price per item/services. This should be considered when finding the financial value (**size**) for each tenant. 

## Tenant Significancies

Tenant significancies to a Mall (financial value) is represented by each tenant's monthly revenue. It will be visualized using the node size later in the Tenants Graph using `visNetwork`.
```{r}
# calculating financial value
# financial value (size) = monthly revenue
size <- dummy %>%
  group_by(Tenant) %>%
  dplyr::summarize(Monthly_Revenue = mean(Revenue)) %>% 
  arrange(desc(Monthly_Revenue)) %>% 
  mutate(size = round(Monthly_Revenue*0.00000001,1))
size
```

## Corelation between Tenants

Correlation between tenants reflect the tenant synergy. We can visualize the correlation of daily sales for each tenant using `ggcorr()` from GGally package:

```{r message=FALSE, warning=FALSE}
# transform long into wide data format
dummy_cor <- dummy %>% 
  select(Tenant,Date,Revenue) %>%
  spread(Tenant,Revenue)
dummy_cor
```

```{r message=FALSE, warning=FALSE}
library(GGally)

ggcorr(dummy_cor[,-1], # do not include the date column 
       label = T, 
       label_size = 2.5, 
       hjust = 1, layout.exp = 5)
```

Transforming corelation result into data frame using `rcorr()` from Hmisc:

```{r message=FALSE, warning=FALSE}
library(Hmisc)
dummy_cor_m <- as.matrix(dummy_cor[,-1])
cor_matrix <- rcorr(dummy_cor_m)

# ++++++++++++++++++++++++++++
# flattenCorrMatrix
# ++++++++++++++++++++++++++++
# cormat : matrix of the correlation coefficients
# pmat : matrix of the correlation p-values

flattenCorrMatrix <- function(cormat) {
  ut <- upper.tri(cormat)
  data.frame(
    Tenant1 = rownames(cormat)[row(cormat)[ut]],
    Tenant2 = rownames(cormat)[col(cormat)[ut]],
    Correlation  =(cormat)[ut]
    )
}

flat_cor <- flattenCorrMatrix(cor_matrix$r) %>% 
  filter(Correlation >= 0.5 | Correlation <= -0.5) # filter the observations which have strong enough correlation

cor_df <- flat_cor %>% 
  mutate(width=ifelse(Correlation>0.5,Correlation,-Correlation),
         width=width^5*10,
         color=ifelse(Correlation>0.5,"Blue","Red"))

cor_df
```

## Visualization Network

The financial value and tenant synergy can be visualized using visNetwork. Prior to visualization, a data pre-processing step is needed to match the column name and format:
```{r}
vn_nodes <- size %>% 
  mutate(id = row_number(size)) %>% 
  rename(label = Tenant,
         value = size) %>% 
  select(id, label, value)

head(vn_nodes) 
```

```{r}
# prepare switching function from tenant name to tenant id
decode <- function(data){
  sapply(as.character(data), switch,
       "Fossil" = "1",
       "Guardian" = "2",
       "Daiso" = "3",
       "Kopi Kenangan" = "4",
       "Sport Station" = "5",
       "Erha Dermatologist" = "6",
       "The Executive" = "7",
       "Pull&Bear" = "8",
       "H&M" = "9",
       "The Body Shop" = "10",
       "Yoshinoya" = "11",
       "Celebrity Fitness" = "12",
       "KOI" = "13",
       "Zara" = "14",
       "Miniso" = "15",
       "Chatime" = "16",
       "Pandora" = "17",
       "CGV" = "18",
       "Uniqlo"= "19",
       "Gramedia" = "20")
}

vn_edges <- cor_df %>%
  rename(from = Tenant1,
         to = Tenant2) %>% 
  mutate(from = decode(from),
         to = decode(to))

head(vn_edges)
```

whereas:
* node: represent each tenant
* node size: represent the financial value of each tenant
* line_width: correlation value (the higher the stronger)
* line_color: correlation value (blue: positive, red: negative)

```{r}
library(visNetwork)
set.seed(100)
visNetwork(nodes=vn_nodes,edges=vn_edges,width="100%") %>%
  visLegend() %>%
  visOptions(nodesIdSelection = T,highlightNearest = T)
```

